\documentclass[12pt]{article}

\usepackage{fullpage}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{upgreek}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
}


\begin{document}

\title{CS2ME3 Assignment 1 report}
\author{Mingnan Su \\ macID: sum1}
\maketitle
\addtocontents{toc}{\protect\hypertarget{toc}{}}
\tableofcontents
\newpage

% 1.your files
\section{My Codes}

\subsection{CircleADT.py}
\lstinputlisting{../src/CircleADT.py}
\newpage

\subsection{Statistics.py}
\lstinputlisting{../src/Statistics.py}
\newpage

\subsection{testCircles.py}
\lstinputlisting{../src/testCircles.py}
\vskip 10cm

\subsection{Makefile}
\lstinputlisting{../Makefile}
\newpage

% 2.partner's files
\hyperlink{toc}{Return to content page.}
\section{Partner Codes}

\subsection{CircleADT.py}
\lstinputlisting{../src/ptnCircleADT.py}
\vskip 5cm

\subsection{Statistics.py}
\lstinputlisting{../src/ptnStatistics.py}
\newpage

% 3.result testing your files
\hyperlink{toc}{Return to content page.}
\section{The result of testing my files}
\lstinputlisting{myOutput.txt}
\newpage

% 4.result testing partner&your files
\hyperlink{toc}{Return to content page.}
\section{The result of testing partner's files}
\lstinputlisting{ptnOutput.txt}
\newpage

% 5.discussion
\hyperlink{toc}{Return to content page.}
\section{Discussion of test results}
Test file works everying OK on my files, partially OK on my partner's file.
\newline Functions that not worked out right on my partner's files are:
\begin{enumerate}
  \item CircleADT.CircleT.insideBox
  \item Statistics.rank
\end{enumerate}

\subsection{What you learned doing the exercise}
I learned many usefull tools by completing this assingment: latex, doxygen, git, etc.
\subsection{List any problem I found with: }
\begin{itemize}
  \item My program
  \newline I didn't use the comment style which could be detected by doxygen.
  \item My partner's module
  \begin{enumerate}
    \item CircleADT.CircleT.insideBox
    \newline In my partner's module, in CircleT class, under the function insideBox, he defines:
    \begin{lstlisting}
    if (self.x>x0 and self.y>y0)
    \end{lstlisting}
    Problem occurs at the second part. The y-coordinate of the center of the circle should always place under y0. In another words, self.y is less than y0
    \item Statistics.rank
    \newline In my partner's module, he implement bubble sort to solve the problem. But inside the loops, he writes:
    \begin{lstlisting}
    for x in range (len(R)):
      for i in range (len(R)):
        if (R[x] > R[i] and Rank[x] > Rank[i])
    \end{lstlisting}
    He should only compare the elements in R, and swap the elements in Rank, instead of compare two lists.
  \end{enumerate}
  \item the specification of the modules
  \newline We might can create another ADT called RectT, which defines a rectangular. Then function insideBox becomes
  \begin{lstlisting}
  def insideBox (rectT)
  \end{lstlisting}
\end{itemize}
\newpage

% 6.discussion
\hyperlink{toc}{Return to content page.}
\section{how I handled the value of $\pi$ in my program}
I import a python package math and use math.pi to generate a $\pi$ value.
\subsection{Why I made this choice}
In this way, I think it's more accurate than I manually type in the value (3.14159)
\subsection{Is $\pi$ explicitly expanded in my formula}
When I use a pi value, I just simply replace it with "math.pi". 
\end{document}
